---
title: "HW1 for comp in biostat and epi"
author: "Gillian Cheng"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
header-includes: \usepackage{titling}
---


## Example 2

In regression analysis, if you observe an F test statistic = 3.2 (right-tailed test), and under the null hypothesis this statistic should follow an F distribution with a numerator d.f. of 3 and a denominator d.f. of 194, please find the p-value? Please plot the pdf and cdf of this F distribution.

### P-value
```{r pval}
pval <- pf(3.2,3,194, lower.tail = F)
paste("The p-val of F-stat = 3.2 under df =c(3,194) is",round(pval,4))
```
```{r pvalplot,include=FALSE, fig.align='center', fig.width=8, fig.height=4}
x <- seq(0,5,0.01)
PDF <- df(x,df1 = 3, df2 = 194)
par(pty="s")
plot(PDF, type = "l", col = "pink", lwd = 3, xlab = "F statistics",
     ylab = "Density function", main = "PDF")

abline(v = 3.2, lwd = 2)
text(200, 0.1, paste("p-value = ", round(pval,3)))
```

### PDF & CDF
```{r PDFCDF,fig.align='center', fig.width=8, fig.height=4}
x <- seq(0,5,0.01)
PDF <- df(x,df1 = 3, df2 = 194);CDF <- pf(x,df1 = 3, df2 = 194)

par(pty="s", mfrow=c(1,2))

plot(PDF, type = "l", col = "pink", lwd = 3, ylab = "Density function", main = "PDF")
plot(CDF, type = "l", col = "pink", lwd = 3, ylab = "Cumulative Probability", main = "CDF")
```

## Example 3

In regression analysis, if you observe a t test statistic = -2.08 (two-tailed test), and under the null hypothesis this statistic should follow a t distribution with a d.f. of 136, please find the p-value? What's the p-value if you observe a t test statistic = 2.45 (two-tailed test). Please plot the pdf and cdf of this t distribution.

### P-value
```{r pval2}
pval1 <- 2 * pt(-2.08, 136)
pval2 <- 2 * pt(2.45, 136, lower.tail = F)
```
```{r out,echo=FALSE}
paste("The p-val of t-stat = -2.08 under df = 136 is",round(pval1,4))
paste("The p-val of t-stat = 2.45 under df = 136 is",round(pval2,4))
```

### PDF & CDF
```{r PDF CDF2,fig.width=8, fig.height=4}
x2 <- seq(-3,3,0.01)
PDF2 <- dt(x2, 136)
CDF2 <- pt(x2, 136)
par(pty="s", mfrow=c(1,2))

plot(PDF2, type = "l", col = "steelblue", lwd = 3,
     ylab = "Density function", main = "PDF")

plot(CDF2, type = "l", col = "steelblue", lwd = 3, 
     ylab = "Cumulative Probability", main = "CDF")
```
