---
title: "HW2 for comp in biostat and epi"
author: "Gillian Cheng"
date: '`r Sys.Date()`'
output:
  html_document:
    df_print: paged
---

## Ex8

There were 50 students in a class. 
All odd-numbered students were boys, and all even-numbered students were girls. 

There were 7 students passing the midterm exam: 11,16,23,31,36,47,50. 
There were 9 students passing the final exam: 3,9,16,20,27,31,36,49,50.

Please use the R commands regarding set operations to answer the following four questions:

```{r}
even <- function(x){subset(x, x %% 2 == 0)}
odd <- function(x){subset(x, x %% 2 != 0)}

mid_pass <- c(11,16,23,31,36,47,50)
final_pass <- c(3,9,16,20,27,31,36,49,50)
```

(1) Please list the boys who passed both the midterm and final exams
```{r}
q1 <- intersect(mid_pass,final_pass)
odd(q1)
```
(2) Please list the girls who passed both the midterm and final exams
```{r}
q2 <- intersect(mid_pass,final_pass)
even(q2)
```
(3) Please list the boys who passed the midterm exam but failed the final exam
```{r}
q3 <- setdiff(mid_pass,final_pass)
odd(q3)
```
(4) Please list the girls who failed the midterm exam but passed the final exam
```{r}
q4 <- setdiff(final_pass, mid_pass)
even(q4)
```

## Ex 9
Please write a function on your own to estimate the regression coefficients of a simple linear regression, where the response variable is “y” from “seizure.csv” (Week 1 course material) and the predictor variable is “lweek” from “seizure.csv”. 

(Hint: the regression coefficients should include an intercept term and a slope term)
```{r}
seizure <- read.csv("seizure.csv")

simple_regression <- function(x,y,data){
        x <- data[[x]]
        y <- data[[y]]
        
        xbar <- mean(x)
        ybar <- mean(y)
        beta_hat <- sum((x-xbar)*(y-ybar))/ sum((x-xbar)**2)
        intercept <- ybar-beta_hat*xbar
        return(list(beta_hat = beta_hat, intercept = intercept))
}

simple_regression(x = "lweek",y = "y", data = seizure)
lm(y ~ lweek, data = seizure)
```