---
title: "HW8comp"
author: "Gillian Cheng"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---
gradient and hessian matrix are used in calculating high-dimentional Newton-Raphson method, these are all route for us to find the best fit for the functions.
Gradient is a column vector with first derivatives of f(x).
Hessian matrix is square matrix filled with  second-order partial derivatives of f(x).
we want our model stable, and the uncertainty of the model and the correlation between the variables can be represented through variance-covariance matrix.

## Ex 20-1:

1. Please use the Newton-Raphson method to find the maximum likelihood estimate (MLE) of the regression coefficients of logistic regression.

```{r, include=FALSE}
newtonraphson <- function(ftn, x0, tol = 1e-9, max.iter = 100) {
        x <- x0        # x0: the initial value
        fx <- ftn(x)
        iter <- 0
        while ((max(abs(fx[[1]])) > tol) & (iter < max.iter)) {
                x <- x - solve(fx[[2]]) %*% fx[[1]]
                fx <- ftn(x)
                iter <- iter + 1
        }
        if (max(abs(fx[[1]])) > tol) {
                cat('Algorithm failed to converge\n')
                return(NULL)
        } else {     # max(abs(fx[[1]])) <= tol
                cat("Algorithm converged\n")
                return(x)
        }
}
```

```{r}
resp <- read.csv("resp.csv")

# A->1, P->0
resp$treatment2 <- ifelse(resp$treatment == "A", 1,
                          ifelse(resp$treatment == "P", 0, NA))


X <- cbind(rep(1,length(resp$outcome)),resp$treatment2, resp$age, resp$baseline)
Y <- resp$outcome

ftn <- function(betacoef){
        pi1 <- exp(X%*%betacoef)/(1+exp(X%*%betacoef))
        gradient <- t(X)%*%(Y-pi1)
        hessian <- -t(X)%*%diag(c(pi1*(1-pi1)),length(resp$outcome))%*%X
        Loglike <- sum(Y*log(pi1/(1-pi1))+log(1-pi1))
        return(list(gradient, hessian, Loglike))
}

```

```{r}
(beta <- newtonraphson(ftn, c(0,0,0,0)))

hh <- glm(outcome ~ treatment2+age+baseline, data= resp, family = binomial)
hh$coefficients
```


2.Please find the variance-covariance matrix for the betas . 
```{r}
solve(-ftn(beta)[[2]])
vcov(hh)
```

3. Please find the log likelihood at the betas . 
```{r}
ftn(beta)[[3]]
logLik(hh)
```
